---
title: "Model results"
author: "Frank Edwards"
date: "September 16, 2016"
output: html_document
---

Apologies for the difficulty in reading the tables, especially the inclusion of the estimated state fixed effects. I'll clean this up for the paper, but wanted to share these results and see if you had any suggestions for modeling. There's some missing data, so I've run MI (only 2 iterations needed), but am only showing results from 1 imputed dataset here. I've checked the combined results, and they are consistent, but with slightly larger SEs - it's a pain to make those into pretty tables, so I'm saving that effort for the full write-up.

Here are a few sets of model results. First, I show the results from negative binomial models of foster care caseloads for African Americans and Native Americans with state fixed effects with a two robustness tests (lagged incarceration, lagged outcome). Second, I show the results from multilevel models of caseload racial inequality with state intercepts. 

These results show:

1. A strong effect on within-state changes in African American and Native American incarceration on foster care caseloads (for Native Americans, clear effect for F incarceration, not so for total, M incarceration). For African Americans, total and Male incarceration clearly related to FC caseloads, no relationship for Female incarceration.
2. A strong effect on within and between state variation in unequal incarceration and unequal foster care caseloads

In my opinion, the remaining data issue to be dealt with is measurement error on Native American population characteristics from the ACS. Some of the measures (HS completion, child poverty), have very obvious measurement error when you look at the time series (very small subpopulations in some states, it's a huge stretch to use ACS one-year data for this (which I've manually constructed into 3-year estimates, better, but still imperfect), better with the multi-year data). I'm thinking about using Gary King's suggestion to over-impute these data, but have also been thinking about going to the stats consultants to get advice on strategies for that. This may be overkill before writing it up, but I think it would improve model fit for the Native American models.

```{r, message=FALSE, warning=FALSE}
source("~/Dropbox/cw-race/models-FE.R")
```

#FE Models, African American caseloads

Negative binomial models of foster care caseloads, offset by child population

- Model 1 with State FE, linear national time effect (have also experimented with year|state slopes, doesn't affect results, mixed impact on model fit)
- Model 2 + lagged incarceration
- Model 3 + lagged caseload

First table, all incarceration, second table, incarceration by gender

```{r, message=FALSE, warning=FALSE, results="asis"}
b.tab
b.gender.tab
```

#FE Models, Native American caseloads

- Model 1 with State FE, linear national time effect
- Model 2 + lagged incarceration
- Model 3 + lagged caseload

First table, all incarceration, second table, incarceration by gender

```{r, message=FALSE, warning=FALSE, results="asis"}
a.tab
a.gender.tab
```

#RE Models, Caseload disproportion

```{r, message=FALSE, warning=FALSE, results="asis"}
b.re.tab
a.re.tab
```
