---
title: "FE model results"
author: "Frank Edwards"
date: "September 25, 2016"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("C:/Users/kilgore/Dropbox/cw-race/")
source("cw-main.R")
```

Below, I present results from within-state estimations of the relationship between incarceration and foster care caseloads and entries for Native Americans and African Americans. I use four strategies for handling measurement error in the ACS 2001-2007, 4 modeling strategies to identify relationships between incarceration and foster care, and 12 relationships between predictors and 4 outcomes (Black FC caseloads/entries, Native American FC caseloads/entries) (192 total models). The results from all models are included as tables below, but I construct a series of forest plots to allow for a relatively easy comparison of model results across specifications.

**Summary**

I include measures for both contemporaneous incarceration and incarceration lagged by one year. Estimates are generally positive. Black incarceration and lagged Native American incarceration are significantly different from zero in most specifications. My preference is to move forward with the overimputation approach and a combination of State and State/Year FE models for one set of analyses, and RE models of inequality outcomes as another set. 

**Four measurement strategies for ACS population estimates:**

ACS 1 year observations (the only population data available for many variables of interest at the state-year level) for 2001-2007 are measured with substantial error for small groups, and time series appear unrealistic (frequent zeroes, unstable trends). I estimate all models using four strategies to handle measurement error induced by small populations and the limits of sample derived population parameters.

```{r, echo=FALSE, results='asis'}
no.imp.plot
post.imp.plot
```




1. Multiple overimputation ((Blackwell et al 2015) for 2001-2006 ACS for states with fewer than 100,000 Black or Native American residents with prior expected value as weighted average of 1 year observation and variably weighted 2000 census and 2009 5-year ACS based on year of imputation.$w_{obs}=0.1$,  $w_{2000}=0.75-0.12(year-2001)$, $w_{2009}=0.9-w_{2000}$. Prior variance is equal to the variance of all state observations 2000-2014 divided by the square root of the number of observations per state (15). N=750
2. Exclude observations prior to 2007, eliminating 1-year ACS data from the analysis, no imputation, reduced N=350
3. Drop all state-years with small Native American or African American populations (total population less than 10,000), N=517
4. Construct 3-year averages from 1-year ACS data for 2001-2006, drop 2001 observation. Multiple imputation with time-series priors for limited missingness, N=700

**12 relationships to test**

I examine 12 relationships between incarceration and foster care at the state-year level for each measurement strategy

1. Black foster care caseloads per capita ~ Black incarceration per capita (all)
2. Black foster care caseloads per capita ~ Black male incarceration per capita
3. Black foster care caseloads per capita ~ Black female incarceration per capita
4. Native American foster care caseloads per capita ~ Native American incarceration per capita (all)
5. Native American foster care caseloads per capita ~ Native American male incarceration per capita
6. Native American foster care caseloads per capita ~ Native American female incarceration per capita 
1. Black foster care entries per capita ~ Black incarceration per capita (all)
2. Black foster care entries per capita ~ Black male incarceration per capita
3. Black foster care entries per capita ~ Black female incarceration per capita
4. Native American foster care entries per capita ~ Native American incarceration per capita (all)
5. Native American foster care entries per capita ~ Native American male incarceration per capita
6. Native American foster care entries per capita ~ Native American female incarceration per capita 

All rates are modeled as either natural logs (if no zeroes are observed), or square roots if zeroes are observed.

*Four modeling strategies*

1. State fixed effects, Panel Corrected Standard Errors (Beck and Katz 1995)
2. State and year fixed effects, includes white incarceration, Panel Corrected Standard Errors (Beck and Katz 1995)
3. First difference
4. Lagged dependent variable (with 2 year lag DV), Panel Corrected Standard Errors (Beck and Katz 1995)

#Visualization of model results across error strategies and modeling strategies

```{r, echo=FALSE}
ForestFE
ForestFEent
ForestRob
ForestRobEnt
ForestLag
ForestLagEnt
ForestFD
ForestFDEnt
```

#Full model results, by error strategy

#Multiple Overimputation, 2000-2014

##Caseloads

Models of log(caseloads) by race for 2000 - 2014

###State Fixed Effects
```{r, echo=FALSE, results='asis', message=FALSE }
library(xtable)
print(xtable(as.data.frame(OI.models$FE.models$b$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.models$b.m$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.models$b.f$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.models$a$merge), caption="Native American FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' , results='asis'}
print(xtable(as.data.frame(OI.models$rob.models$b$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.models$b.m$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.models$b.f$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.models$a$merge), caption="Native American FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(OI.models$fd.models$b$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.models$b.m$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.models$b.f$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.models$a$merge), caption="Native American FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(OI.models$lag.models$b$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.models$b.m$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.models$b.f$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.models$a$merge), caption="Native American FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

##Entries

Models of foster care entries (logged) by race

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(OI.models$FE.ent.models$b$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.ent.models$b.m$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.ent.models$b.f$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.ent.models$a$merge), caption="Native American FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(OI.models$FE.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(OI.models$rob.ent.models$b$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.ent.models$b.m$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.ent.models$b.f$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.ent.models$a$merge), caption="Native American FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(OI.models$rob.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(OI.models$fd.ent.models$b$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.ent.models$b.m$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.ent.models$b.f$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.ent.models$a$merge), caption="Native American FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.ent.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(OI.models$fd.ent.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(OI.models$lag.ent.models$b$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.ent.models$b.m$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.ent.models$b.f$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.ent.models$a$merge), caption="Native American FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.ent.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(OI.models$lag.ent.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

#Excluding pre-2007 observations

##Caseloads

Models of log(caseloads) by race for 2000 - 2014

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$FE.models$b$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.models$b.m$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.models$b.f$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.models$a$merge), caption="Native American FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$rob.models$b$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.models$b.m$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.models$b.f$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.models$a$merge), caption="Native American FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$fd.models$b$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.models$b.m$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.models$b.f$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.models$a$merge), caption="Native American FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$lag.models$b$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.models$b.m$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.models$b.f$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.models$a$merge), caption="Native American FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

##Entries

Models of foster care entries (logged) by race

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$FE.ent.models$b$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.ent.models$b.m$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.ent.models$b.f$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.ent.models$a$merge), caption="Native American FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(No1yr.models$FE.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$rob.ent.models$b$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.ent.models$b.m$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.ent.models$b.f$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.ent.models$a$merge), caption="Native American FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(No1yr.models$rob.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$fd.ent.models$b$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.ent.models$b.m$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.ent.models$b.f$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.ent.models$a$merge), caption="Native American FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.ent.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(No1yr.models$fd.ent.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(No1yr.models$lag.ent.models$b$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.ent.models$b.m$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.ent.models$b.f$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.ent.models$a$merge), caption="Native American FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.ent.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(No1yr.models$lag.ent.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

#No small population (African American, Native American) states

##Caseloads

Models of log(caseloads) by race for 2000 - 2014

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$FE.models$b$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.models$b.m$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.models$b.f$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.models$a$merge), caption="Native American FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$rob.models$b$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.models$b.m$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.models$b.f$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.models$a$merge), caption="Native American FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$fd.models$b$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.models$b.m$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.models$b.f$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.models$a$merge), caption="Native American FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$lag.models$b$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.models$b.m$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.models$b.f$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.models$a$merge), caption="Native American FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

##Entries

Models of foster care entries (logged) by race

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$FE.ent.models$b$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.ent.models$b.m$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.ent.models$b.f$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.ent.models$a$merge), caption="Native American FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(drop.models$FE.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$rob.ent.models$b$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.ent.models$b.m$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.ent.models$b.f$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.ent.models$a$merge), caption="Native American FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(drop.models$rob.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$fd.ent.models$b$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.ent.models$b.m$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.ent.models$b.f$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.ent.models$a$merge), caption="Native American FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.ent.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(drop.models$fd.ent.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(drop.models$lag.ent.models$b$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.ent.models$b.m$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.ent.models$b.f$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.ent.models$a$merge), caption="Native American FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.ent.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(drop.models$lag.ent.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

#Untransformed 3-year estimates for 2001-2006

##Caseloads

Models of log(caseloads) by race for 2000 - 2014

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$FE.models$b$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.models$b.m$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.models$b.f$merge), caption="Black FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.models$a$merge), caption="Native American FC Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$rob.models$b$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.models$b.m$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.models$b.f$merge), caption="Black FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.models$a$merge), caption="Native American FC Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$fd.models$b$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.models$b.m$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.models$b.f$merge), caption="Black FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.models$a$merge), caption="Native American FC Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$lag.models$b$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.models$b.m$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.models$b.f$merge), caption="Black FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.models$a$merge), caption="Native American FC Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

##Entries

Models of foster care entries (logged) by race

###State Fixed Effects
```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$FE.ent.models$b$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.ent.models$b.m$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.ent.models$b.f$merge), caption="Black FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.ent.models$a$merge), caption="Native American FC Entries (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
print(xtable(as.data.frame(MI.models$FE.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State FE"), type="html")
```

###State and year fixed effects

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$rob.ent.models$b$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.ent.models$b.m$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.ent.models$b.f$merge), caption="Black FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.ent.models$a$merge), caption="Native American FC Entries (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.ent.models$a.m$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
print(xtable(as.data.frame(MI.models$rob.ent.models$a.f$merge), caption="Native American Caseloads (logged), with State & Year FE"), type="html")
```


###First difference

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$fd.ent.models$b$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.ent.models$b.m$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.ent.models$b.f$merge), caption="Black FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.ent.models$a$merge), caption="Native American FC Entries (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.ent.models$a.m$merge), caption="Native American Caseloads (logged), first difference"), type="html")
print(xtable(as.data.frame(MI.models$fd.ent.models$a.f$merge), caption="Native American Caseloads (logged), first difference"), type="html")
```


###Lagged DV

```{r, echo=FALSE, results='asis' }
print(xtable(as.data.frame(MI.models$lag.ent.models$b$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.ent.models$b.m$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.ent.models$b.f$merge), caption="Black FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.ent.models$a$merge), caption="Native American FC Entries (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.ent.models$a.m$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
print(xtable(as.data.frame(MI.models$lag.ent.models$a.f$merge), caption="Native American Caseloads (logged), lagged DV"), type="html")
```

